---
name: Andy Kleinhesselink
position: "Quantitative Ecologist"
address: "Ecology and Evolutionary Biology, UCLA"
phone: +1 310 825-4967
#web: "https://github.com/akleinhesselink/"
email: "arklein@ucla.edu"
github: akleinhesselink
researchgate: Andrew Kleinhesselink
linkedin: andrew-kleinhesselink-6116b294
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::moderncv:
    theme: classic
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(glue)
library(lubridate)
library(rorcid)
library(scholar)
```



```{r loadData}
# Job titles
job.titles <- read_csv("../data/job-titles.csv",
                      col_types = cols(
                        begin = col_date("%m/%d/%y"),
                        end = col_date("%m/%d/%y")
                        )
)


job.titles$end[is.na( job.titles$end)] <- today()

job.titles <- 
  job.titles %>% 
  filter(is.na(end) | year(end) > 2007 | jobId == 6 )

# Job descriptions
job.descriptions <- read_csv("../data/job-descriptions.csv")

awards <- read_csv("../data/awards.csv")

manuscripts <- read.csv('../data/manuscripts.csv')

presentations <- read_csv('../data/presentations.csv')

peer_reviews <- read_csv('../data/peer_reviews.csv') 

in_press <- read.csv('../data/in_press.csv')


```



# Education

```{r education}

edu <- rorcid::orcid_educations("0000-0003-2149-2027")

edu$`0000-0003-2149-2027`$`education-summary` %>% 
  mutate(`end-date.year.value` = replace_na(`end-date.year.value`, "2019")) %>% 
  detailed_entries(
    what = `role-title`,
    when = glue::glue("{`start-date.year.value`}--{`end-date.year.value`}"), 
    with = organization.name,
    where = glue("{organization.address.city}, {organization.address.region}")
  )
```


# Experience

```{r experience}

job.titles %>% 
  left_join(job.descriptions) %>% # Join job descriptions 
  arrange(desc(end)) %>%   # Arrange by descending end date
  detailed_entries(   # Format as detailed entries
    what = position,
    when = as.character(
      glue("{year(begin)} - {if_else(end != today(), as.character(year(end)), 'present')}")),
    with = employer,
    where = glue("{city}, {region}"),
    why = accomplishments)

```


# Publications

```{r publications}
get_publications("Hv1P9zYAAAAJ") %>%
  filter( number != '' ) %>%
  bind_rows(in_press) %>% 
  arrange(desc(year))  %>%
  detailed_entries(
    what = title,
    when = year,
    with = author,
    where = journal
  )
```

# Manuscripts in Preparation

```{r manuscripts }

manuscripts %>%
  detailed_entries(
    what = title,
    with = author,
    where = status
  )
```


# Presentations

```{r presentations}

presentations %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = When,
                   with = Conference,
                   where = Location)

```


# Grants and Fellowships
```{r awards}
awards %>% 
  filter( !str_detect(title, "(John)|(Ralph)") ) %>% 
  brief_entries(
    what = title,
    when = year)
```

# Teaching and Mentoring
- Instructor for Software Carpentry: (https://software-carpentry.org/)
  - Teach lessons on Shell, Git and R for data analysis and data visualization
  - Organized workshop for [UCLA EEB, April 7th, 2017.](https://ucla-data-archive.github.io/2018-04-07-ucla-eeb/)
- Undergraduate mentoring 
  - Undergraduate student research projects in Kraft Lab at UCLA.
  - NSF REU projects in Adler Lab at USU.
- Ecological Society of America SEEDS Mentor. August 2012.
  - Undergraduate mentor for ESA Annual meeting. 


# Service and Outreach 

- Peer reviewer: AoB Plants (3), Ecology Letters (4), Journal of Vegetation Science (2), The American Naturalist (3), New Phytologist (2), Dendrochronologia (1), Ecology (1), Functional Ecology (1), Global Ecology and Biogeography (2), Oecologia (1), Plos One (1), Biological Invasions (1), Ecography (1), Ecosphere (1), Methods in Ecology and Evolution (1), Plant Ecology and Diversity (1), Plant and Soil (1), NSF DEB Grants (1)
- Board Member, UCLA Bruin Naturalist Club, 2018-2019.
  - Organized and led natural history field trips for undergraduates. 
- Co-Chair of USU Ecology Center Seminar Committee. 2013-2014.
- Vice President San Francisco Nature Education 2009-2010.
  - Led environmental education lessons for students at underserved elementary schools.
- Contributor to iNaturalist: https://www.inaturalist.org/people/andy71
- Contributor to eBird: https://ebird.org/profile/MTM5OTI2/US-CA-037

# Computational Skills 

- R: Statistical analysis, data visualization, simulation modeling
- STAN: Bayesian modeling 
- Git: Version control
- Python, NumPy and SciPy 



